%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Zoomit}{Apr 2021 -- Present}
    {Technical lead}{Tehran, Iran}
    \resumeItemListStart
        \resumeItem{Zoomit is the most viewed Persian-language media in the field of technology with over 25M views a month. }
        \resumeItem{Managed and led 6 engineers and helped them to thrive in their careers by executing a together learning program every sprint and One-on-One meetings which leads to higher morale.}
        \resumeItem{Helping the company move towards cloud native by configuring and leveraging CNCF approved technologies for deployment, logging, and collecting metrics like Gitlab CI, Docker, Elastic APM, Prometheus, and Kubernetes.}
        \resumeItem{Using different rendering patterns and caching strategies. Our performance test with locust results in 2k+ rps.}
        \resumeItem{Maintained a large NX Monorepo with 20 applications and libraries including Design systems, Unit and E2E test, shared components, and utils.}
        \resumeItem{Developed a server driven UI module system for dynamic content and advertisement without content jump.}
        \resumeItem{Architect a state of the art block editor with over 25 blocks (typography, image, table, related-articles, quote) empowering 100+ writers. Decoupled the blocks JSON specification from UI to achieve end-to-end type-safety, tree shaking, and rendering different UIs based on templates.}
        \resumeItem{Delivering high quality features on time to this day. With the help of sympathetic colleagues and solid architecture.}
    \resumeItemListEnd
    
    \resumeSubheading
    {iGap Messenger}{Jun 2020 -- Apr 2021}
    {Software Engineer}{Tehran, Iran}
    \resumeItemListStart
        \resumeItem{iGap is a free and partially open-source end-to-end encrypted instant messaging. It has 15M+ downloads. Our mission was to rewrite the client using modern technologies like React, Typescript, Redux, WebSocket, and MUI.}
        \resumeItem{Built voice \& video calling using WebRTC with support for ringing, muting, and disabling for enhanced control.}
        \resumeItem{Added support for Bots. }
        \resumeItem{Worked on sticker and animated sticker using Samsung's rlottie WASM bindings. It improved CPU performance by 76\% and ensured 60fps for low-end devices. Our PWA implementation performed better than the native Android.}
        \resumeItem{Implemented several proto message handlers: Reply and Forward message, create and manage Channels and Groups, Profile (bio, privacy settings, notifications), iLand (server driven tiles with deep links and different actions)}
    \resumeItemListEnd

    \resumeSubheading
    {Mine taxi}{Dec 2019 -- May 2020}
    {Software Engineer}{Tehran, Iran}  
    \resumeItemListStart
        \resumeItem{MineTaxi is a ride-sharing startup. Their focus is on the small towns.}
        \resumeItem{Developed the web application using React, Sass and Redux. Built reusable components for other developers.}
    \resumeItemListEnd

\resumeSubHeadingListEnd